Program Transformations for miniKanren

### 2020-07-07 papers/aplas/text/abstract.tex
Abstract

\begin{abstract}
  We explore partial deduction for \mk: a specialization technique aimed at improving the performance of a relation in the given direction.
  We describe a novel approach to specialization of \mk based on partial deduction and supercompilation.
  On several examples, we demonstrate issues which arise during partial deduction.
\end{abstract}

>>>>

\begin{abstract}
  We study conjunctive partial deduction, an advanced specialization technique aimed at improving the performance of logical programs, in the context of relational programming language \mk. We identify a number of issues, caused by  \mk pecularities, and describe a novel approach to specialization based on partial deduction and supercompilation. While the results of the evaluation do not yet demonstrate the advantages of our approach in all cases, we nevertheless consider it as the first step towards an efficient optimization framework for \mk.
\end{abstract}
